CSCI 580 : Monte Carlo Path Tracing

### 2015-11-27 paper/paper.tex
actual bibliography: first 2 sources formatted

% SAMPLE BIBLIO

SAMPLE BIBLIOGRAPHY

\begin{thebibliography}{4}

\bibitem{Pottinger}
Pottinger, D.C. 2005 Terrain Analysis in Realtime Strategy Games, \emph{Ensemble Studios}.
\\
\bibitem{Johan}
Hagelb\"ack, J., and Johansson, S. J. 2008. Using multiagent
potential fields in real-time strategy games. In
Padgham, L., and Parkes, D., eds., \emph{Proceedings of the Seventh
International Conference on Autonomous Agents and
Multi-agent Systems (AAMAS)}.
\\
\bibitem{Thurau}
Thurau, C., and Bauckhage C. 2004. Learning human-like Movement Behavior for
Computer Games. \emph{Gerhard Sagerer Applied Computer Science,
Bielefeld University}.
\\
\bibitem{Johan_2}
Hagelb\"ack, J., and Johansson, S. J. 2008. The Rise of Potential Fields in Real Time Strategy Bots. In \emph{ Proceedings of the 4th Conference on Artificial Intelligence and Interactive Digital Entertainment (AIIDE)}.
\end{thebibliography}

>>>>

\begin{thebibliography}{2}

\bibitem{Appel}
Appel, A. Some techniques for shading machine renderings of solids. \emph{AFIPS '68 (Spring) Proceedings of the April 30--May 2, 1968, spring joint computer conference}: pp. 37-45, 1968.

\bibitem {Whitted}
 Whitted, T. An improved illumination model for shaded display. \emph{Comunications of the AMC}, 23(6):343–349, 1980.

\end{thebibliography}
